Dispersion Distance and the Matter Distribution of the Universe in Dispersion Space

### 2015-06-04 writeup/dm_space_distortions.tex
As posted.

\documentclass[twocolumn,prl,floatfix]{revtex4-1}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{color}
\usepackage{verbatim}
\usepackage{times}
\usepackage{afterpage}
\usepackage{epstopdf}
\usepackage{url}
\usepackage{hyperref}

@@

%\title{The large-scale structure of the Universe in dispersion measure space}
\title{Dispersion distance and the matter distribution of the Universe in dispersion space}

@@

Finally, we note that alone or by combination of dispersion-space data with redshift-space data on a subset of the population, independent redshift surveys of large-scale-structure, or gravitational lensing data could yield very powerful probes of cosmology.   Cosmological dispersion-space data could open a new window on to the structure of the Universe.

>>>>

\documentclass[twocolumn,nofootinbib,prl,floatfix]{revtex4-1}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{color}
\usepackage{verbatim}
\usepackage{times}
\usepackage{afterpage}
\usepackage{epstopdf}
\usepackage{url}
\usepackage{hyperref}

@@

%\title{The large-scale structure of the Universe in dispersion measure space}
\title{Dispersion Distance and the Matter Distribution of the Universe in
Dispersion Space}

@@

Finally, we note that alone---or in combination with
redshift data on a subset of the population, independent redshift surveys,
or gravitational lensing surveys---dispersion-space surveys could yield very
powerful probes of cosmology. Cosmological dispersion-space data could open a
new window into the structure of the Universe.
